Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
minor
macros for displaying Scala code
cite scala overview

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,journal,a4paper]{IEEEtran}
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}

@@

\IEEEPARstart{T}{he} aim of this research is to propose a new sound
and tractable type-theoretic foundation of Scala and languages like
it: the Dependent Object Types calculus (DOT). The properties we are
interested in modeling are Scala's path-dependent types and abstract
type members, as well as its mixture of nominal and structural typing
through the use of refinement types. Compared to previous
approaches~\cite{nuObj,FS}, we make no attempt to model inheritance or
mixing composition. Furthermore, the calculus is more normative than
descriptive, in that it does not precisely describe what's currently
in Scala.

@@

In terms of theoretical results, there's a sketch of soundness in the
paper, but it's unclear whether it is correct. In particular, the
substitution lemma does not seem valid when null is the value to be
substituted and the expression has a type which contains the variable
to be substituted. In the follow-up paper~\cite{tribalo}, the
soundness proof sketch seems more plausible but then is tied to the
ownership system formalism. Decidability and completeness of subtyping
has not yet been established.

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,journal,a4paper]{IEEEtran}

\input{macros}

% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}

@@

\IEEEPARstart{T}{he} aim of this research is to propose a new sound
and tractable type-theoretic foundation of Scala~\cite{ScalaOverview} and languages like
it: the Dependent Object Types calculus (DOT). The properties we are
interested in modeling are Scala's path-dependent types and abstract
type members, as well as its mixture of nominal and structural typing
through the use of refinement types. Compared to previous
approaches~\cite{nuObj,FS}, we make no attempt to model inheritance or
mixing composition. Furthermore, the calculus is more normative than
descriptive, in that it does not precisely describe what's currently
in Scala.

@@

In terms of theoretical results, there's a sketch of soundness in the
paper, but it's unclear whether it is correct. In particular, the
substitution lemma does not seem valid when null is the value to be
substituted and the expression has a type which contains the variable
to be substituted. In the follow-up paper~\cite{tribalo}, the
soundness proof sketch seems more plausible but then is tied to the
ownership system formalism. Decidability of subtyping, and hence
typechecking, has not yet been established.
